
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %%
%% LaTeX to get the ``??'' replaced with the number of the last page  %%
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}
\usepackage{verbatim} 
% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}
    {\minipage[t]{\linewidth}\list{}{%
        \setlength{\leftmargin}{\bibhang}%
        \setlength{\itemindent}{-\leftmargin}%
        \setlength{\itemsep}{\bibsep}%
        \setlength{\parsep}{\z@}%
        }}
    {\endlist\endminipage}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

% 

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{LILIANA E.~FERRUA VILLANUEVA}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{1.85in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
%\href{http://www.ece.osu.edu/}
{\textbf{Liliana E. Ferrua Villanueva}} 				& Cell: (51) 976-739-876\\
%\href{http://www.upenn.edu/}{The University of Pennsylvania}
Calle Salamanca 216									& E-mail:\\ 
Pueblo Libre, Lima 21 Peru							& \href{mailto:lilianaferrua@gmail.com}{\textbf{lilianaferrua@gmail.com}}\\

%& %\textit{WWW:}
%\href{http://www.tedpavlic.com/}{www.tedpavlic.com}\\
\end{tabular}

%\section{Citizenship}
%
%Peruvian

\section{Professional Interests}
%
Textile Engineering, Project Management, Fashion Merchandising, Method Engineering, Business Process Re-engineering  

\section{Education}
%
\href{http://www.uni.edu.pe}{\textbf{National University of Engineering - www.uni.edu.pe}}
\hfill \textbf{Lima, Peru}
\begin{outerlist}
\item[] \href{http://fiqt.uni.edu.pe/home/index.php/escuelas-profesionales/ingenieria-textil}{\textbf{B.S. Textile Engineering}} 
        \hfill \textbf{Aug. 2004 - Dec. 2010}

        \begin{innerlist}
        \item Valedictoriam.
        \item 69 units - 208 credits
        \item Graduated with Honors in Engineering.
        \item Focus on Business Management.\\
        \end{innerlist}
\end{outerlist}

\href{http://www.cip.org.pe}{\textbf{College of Engineers of Peru - www.cip.org.pe}}
\hfill \textbf{Lima, Peru}
\begin{outerlist}
\item[] \href{http://www.cip.org.pe}{\textbf{Seminar - Diploma}}
		\hfill \textbf{2011}
        	\begin{innerlist}
        	\item {Integrated Management Systesm for the Quality, Environment, Occupational Health, Safety and Social Responsibility}
        	\item Valedictoriam.
        	\end{innerlist}
\end{outerlist}

\section{Awards}
%
%\textbf{Awesomeness Award} 
%	\begin{innerlist}
%		\item Smartest Girl EVAAAAA!!!!!!!\\
%	\end{innerlist}
\href{http://www.uni.edu.pe}{\textbf{National university of Engineering}}
	\begin{innerlist}
		\item Valedictoriam \hfill \textbf{2004-2010}\\ 
	\end{innerlist}

\section{Current Projects}
%
%\textbf{Rocking!!!!}
%\begin{innerlist}
%\item Being Sexy!!!\\
%\end{innerlist}
%%------------WLSME----------------%%
\href{http://wlsme.org}{\textbf{Sector 3 Social Venture Group NGO}}
\hfill \textbf{Arequipa, Peru}\\
\href{http://wlsme.org}{http://wlsme.org}
\begin{outerlist}
\item[] \textbf{Project Manager}
    \hfill \textbf{June 2014}
    \begin{innerlist}
        \item Coordinate and supervise the Women´s Leadership in Small and Medium Enterprises Program (WLSME). 
        \item Provide technical consulting to businesswomen in leadership, costs, business management, human resources, and marketing.
		\item Evaluate the businesswoman' progress and the impact in their business: sales increases and business management.
		\item Analysis of the program's reach and impact on their participants and their community.\\  
    \end{innerlist}
\end{outerlist}

%\newpage
\section{Past Work Experience}
%%------------ALLPA S.A.C.----------------%%
\href{http://www.allpaperu.com/en/index.html}{\textbf{ALLPA S.A.C.}}
\hfill \textbf{Lima, Peru}\\
\href{http://www.allpaperu.com}{http://www.allpaperu.com}

\begin{outerlist}
\item[] \textbf{Chief of the Textile Area}
    \hfill \textbf{June 2012 - October 2013}
    \begin{innerlist}
        \item Promoted synergy, decision-making, team work and accountability in the Textile Department. 
        \item Designed and oversaw the execution of the department production plan. 
        \item Developed and managed performance indicators to assess customer satisfaction. 
        \item Particiaped in long-term decision plans for the company.
        \item Supervised the performance of Textile area staff.
        \item Designed a framework for evaluation of current and prospective material suppliers. 
        \item Re-engineer the business process through updating and adhering to new production standards and workflows. 
    \end{innerlist}
 	\textbf{Accomplishments}
 	\begin{innerlist}
 		\item Duplicated sales volume in 2012 and increased the portfolio of clients.\\ 
 	\end{innerlist}   
\end{outerlist}

%%------------BELCORP----------------%%
\href{http://www.belcorp.biz}{\textbf{BELCORP}}
\hfill \textbf{Lima, Peru}\\
\href{http://www.belcorp.biz}{http://www.belcorp.biz}

\begin{outerlist}
\item[] \textbf{Quality Mangement Assistant}
    \hfill \textbf{Dec. 2010 - Apr. 2012}
    \begin{innerlist}
        \item Supervised and improved the production workflows and methods. 
        \item Evaluated and updated the production quality to keep up with international standards for exportation.        
        \item Quality control testing and analysis of raw material and final product (shrinkage, twisting, weight, appearance, strength tests).
		\item Put in place a quality control framework requiring defined procedures, manuals and guidelines. 
		\item Participated in the auditing process to suppliers.\\ 
    \end{innerlist}
\end{outerlist}

%%------------UFITEC----------------%%
\href{http://www.ufitec.com.pe}{\textbf{UFITEC S.A.C.}}
\hfill \textbf{Lima, Peru}\\
\href{http://www.ufitec.com.pe}{http://www.ufitec.com.pe}

\begin{outerlist}
\item[] \textbf{Production Assistant} 
    \hfill \textbf{Nov. 2007 - Aug. 2008}
    \begin{innerlist}
        \item Designed, carried out and assesed the efficacy of improvement plans to increase textile production in the following sectors: cutting, dressmaking, embroidery, apparel printing and sales. 
        \item Put in place the documentation system and created specification sheets for various garments (industrial uniforms, multi-pocket vest, overalls, waterproof jacket, among others) and for their materials' accoutrements.
		\item Execute a cost and financial analysis of garment production.
		\item Applied Method Engineering to create an adaptive framework focused on the production process timeframe.
		\item Optimized the Quality Control process for garment production.
		\item Implemented and supervised an inventory tracking system of final product, raw materials and production equipment.\\  
    \end{innerlist}
\end{outerlist}
%%------------AIRIHUAY S.A.C.----------------%%
\href{http://google.com}{\textbf{AIRIHUAY S.A.C.}}
\hfill \textbf{Lima, Peru}\\
\href{http://www.ufitec.com.pe}{http://www.ufitec.com.pe}

\begin{outerlist}
\item[] \textbf{Consultant}
    \hfill \textbf{Dec. 2007 - Feb. 2008}
    \begin{innerlist}
        \item Program dedicated to recruiting, retaining, and promoting low-income women in entrepreneurial roles.   
        \item Provided technical assessment and consulting services for textile micro-enterprises. 
        \item Technically trained newly created micro-enterprises in quality control of raw material for production.
        \item Enhance the professional skills of businesswomen in the textile sector.
    \end{innerlist}
\end{outerlist}
%
\newpage
\section{Leadership Role}
\href{https://www.facebook.com/CEFIQT?fref=ts}{\textbf{Students Center of the Chemistry and Textile Department}}\\
%\hfill \textbf{Lima, Peru}\\
%\href{https://www.facebook.com/CEFIQT?fref=ts}{https://www.facebook.com/CEFIQT?fref=ts}
\begin{outerlist}
\item[] \textbf{Vice President}
    \hfill \textbf{Nov. 2008 - Aug. 2009}
    \begin{innerlist}
        \item Elected member by the student body to represent them in the organization of departmental activities.
        \item Organized social activities for the student body: concerts, contests, intramurals sports programs, etc. 
        \item Oversee and approve student participation in national congresses and seminars to complement the academic and professional student's formation.\\ 
	\end{innerlist}
\end{outerlist}

\href{https://www.facebook.com/Tefiqt?fref=ts}{\textbf{Students Board at the Chemistry and Texile Engineering Department}}%\hfill \textbf{Lima, Peru}\\ Tercio
%\href{https://www.facebook.com/Tefiqt?fref=ts}{https://www.facebook.com/Tefiqt?fref=ts}

\begin{outerlist}
\item[] \textbf{Student Board Member}
    \hfill \textbf{June 2006 - June 2008}
    \begin{innerlist}
        \item Elected member by the student body to take decisions over the curricula, disciplinary code and strategic plans determined at the Faculty Council (formed by the Dean, Faculty representatives and Student Board Members).
		\item Approved academic related issues like student internship reports, academic year budget and summer classes.
    \end{innerlist}
    \textbf{Accomplishments}
 	\begin{innerlist}
 		\item Involvement in the decision process to create a new master program.\\ 
 	\end{innerlist} 
\end{outerlist}

\section{Extra-Curricular}
\textbf{Women University Volleyball Team}
%\hfill \textbf{Lima, Peru}\\
%\href{https://www.facebook.com/CEFIQT?fref=ts}{https://www.facebook.com/CEFIQT?fref=ts}
%\begin{outerlist}
%\item[] \textbf{Captain}
%    \hfill \textbf{Nov. 2008 - Aug. 2009}
    \begin{innerlist}
        \item Represented the University in tournaments.
	\end{innerlist}
%\end{outerlist}

\section{References}
\textbf{Socialogist Nelly Canepa Moscoso}
\hfill \href{http://www.allpaperu.com}{\textbf{Allpa S.A.C.}}\\
Operations Manager / General Director\\
\href{mailto:ncanepa@allpa.com.pe}{ncanepa@allpa.com.pe}\\

\textbf{M.Eng. Liliana Granados Rutty}
\hfill \href{http://www.belcorp.biz}{\textbf{Belcorp}}\\
Head of the Quality Management Department\\
\href{mailto:lgranados@belcorp.biz}{lgranados@belcorp.biz}\\ 

\textbf{M.Eng. Martin Reaño}
\hfill \href{http://www.sni.org.pe/}{\textbf{Sociedad Nacional de Industrias}}\\
Textile Committee Manager\\ 
\href{mailto:mreano@sni.org.pe}{mreano@sni.org.pe}\\

\textbf{Eng. Segundo Arroyo Gastelu}
\hfill \href{http://www.uni.edu.pe}{\textbf{National University of Engineering}}\\
Professor / Textile Consultant\\
\href{mailto:octavios_1904@hotmail.com}{octavios\_19104@hotmail.com}\\
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
